A distance metric between histograms through the the Kolmogorov-Smirnov test statistic: specification, measures reference and example uses

### 2015-10-31 paper.tex
adicinadas tabelas melhoradas
melhoradas tabelas de audio e musica
terminada polida nas tabelas
terminada polida na parte final

\input{tables/textsGeneral}
\input{tables/textsDistances}
\input{tables/textsDistances2}
\input{tables/textsDistances2b}
\input{tables/textsDistances3}
\input{tables/textsDistances4}
\input{tables/textsDistances4b}

@@

\input{tables/audioGeneral}
\input{tables/audioDistances}

@@

\input{tables/musicGeneral}
\input{tables/musicDistances}

\FloatBarrier
\section{OS status}
This last example expose the statistic $c$ for samples drawn from
the operational system of my laptop.
The patterns are less neat than on last examples,
but many conclusions can still be reached.
The memory used by the most consuming processes compose
the samples which present the highest values of $c$.
Lowest values of $c$ are related to RAM usage.
Again, the type of samples are mandatory:
they might all be identified by the values of $c$
found in comparison to other samples,
with the exception of the RAM memory.
\input{tables/osGeneral}
\input{tables/osDistances}

\FloatBarrier
\section{Conclusions}\label{sec:conc}
The $c$ metric is robust both to determine if
the distributions underlying the samples are the same
and to quantify the difference between probability distributions
through the samples.
The benchmarks for $c$, given in Section~\ref{sec:simulations},
are useful as references to make sense e.g. of the example analysis
of Section~\ref{sec:empirical}.
This is specially useful for the analysis of real phenomena
without any of the training or clusterization usually involved in
classification routines.
The rendering of this article, and all tables,
is automated through Python scripts in order to ease modifications
such as the use of other distributions
and data, or modifications on the measure of $c$.

@@

\appendix
\section{Software and data specifications}\label{ap:soft}
The measure of $c$ is implemented in a small function within
the gmane Python package~\cite{gmanePack}.
The routines for generating the tables from simulated and empirical
data are grouped in separated files for easing further use.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\nocite{*}
\bibliography{paper}% Produces the bibliography via BibTeX.

>>>>

\input{tables/textsGeneral_}
\input{tables/textsDistances_}
\input{tables/textsDistances2_}
\input{tables/textsDistances2b_}
\input{tables/textsDistances3_}
\input{tables/textsDistances4_}
\input{tables/textsDistances4b_}

@@

\input{tables/audioGeneral_}
\input{tables/audioDistances_}

@@

\input{tables/musicGeneral_}
\input{tables/musicDistances_}

\FloatBarrier
\section{OS status}
This last example expose the statistic $c$ for samples drawn from
the operational system of my laptop.
The patterns are less neat than on last examples,
but many conclusions can still be reached.
The memory used by the most consuming processes compose
the samples which present the highest values of $c$.
Lowest values of $c$ are related to RAM usage.
Again, the type of samples are mandatory:
they might all be identified by the values of $c$
found in comparison to other samples,
with the exception of the RAM memory.
\input{tables/osGeneral_}
\input{tables/osDistances_}

\FloatBarrier
\section{Conclusions and automation of the benchmarks}\label{sec:conc}
The $c$ statistic is robust both to determine if
the distributions underlying the samples are the same
and to quantify the difference between such probability distributions.
The benchmarks for $c$, given in Section~\ref{sec:simulations},
are very useful as references to make sense of data 
e.g. as the example analyses of Section~\ref{sec:empirical}.
Notice that the calculations require no
training or clusterization usually involved in
classification routines.

The rendering of this article and all tables
are automated through Python scripts
in order to ease the scrutinization of different settings~\cite{gmanePack}.
After some exploration of  the results,
the setting of
$N_c=100$ comparisons per measure,
$n=n'=1000$ elements in each sample,
$N_b=30$ equally spaced bins was settled
as the template of this document.
The main reason for this choice is that
the results are consistent and stable,
but are still of very modest scales.
The use of more bins 
should enhance the results with respect to generality.
On the other hand, samples are often not so big,
which favors reporting the tables with a small sample size.

%The $c$ statistic is implemented in a small function within
%the Gmane Python package~\cite{gmanePack}.
%The routines for generating the tables from simulated and empirical
%data are grouped in separated files to ease further use.

@@

%\appendix
%\section{Software and data specifications}\label{ap:soft}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\nocite{*}
\bibliography{paper}% Produces the bibliography via BibTeX.

### 2015-10-31 tables/tabNormNull.tex
terminada polida na parte final

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 3 & 3 & 9 \\\hline
5.0 & 0.050 & 1.36 & 1 & 2 & 3 \\\hline
2.5 & 0.025 & 1.48 & 0 & 0 & 2 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for significance levels $\alpha$.
The $c_1$ values were calculated using simulations of normal distributions with $\mu=0$ and $\sigma=1$.
The $c_2$ values were calculated using simulations of normal distributions with $\mu=3$ and $\sigma=2$.
The $c_3$ values were calculated using simulations of normal distributions with $\mu=6$ and $\sigma=3$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.6527$ and $\sigma(c_1)=0.2398$,
 $\mu(c_2)=0.6889$ and $\sigma(c_2)=0.2397$,
 $\mu(c_3)=0.7184$ and $\sigma(c_3)=0.2811$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
100.0 & 0.100 & 1.22 & 73 & 77 & 87 \\\hline
50.0 & 0.050 & 1.36 & 37 & 34 & 49 \\\hline
25.0 & 0.025 & 1.48 & 20 & 13 & 15 \\\hline
10.0 & 0.010 & 1.63 & 7 & 8 & 4 \\\hline
5.0 & 0.005 & 1.73 & 4 & 5 & 2 \\\hline
1.0 & 0.001 & 1.95 & 1 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for significance levels $\alpha$.
The $c_1$ values were calculated using simulations of normal distributions with $\mu=0$ and $\sigma=1$.
The $c_2$ values were calculated using simulations of normal distributions with $\mu=3$ and $\sigma=2$.
The $c_3$ values were calculated using simulations of normal distributions with $\mu=6$ and $\sigma=3$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.8038$ and $\sigma(c_1)=0.2570$,
 $\mu(c_2)=0.8118$ and $\sigma(c_2)=0.2597$,
 $\mu(c_3)=0.8234$ and $\sigma(c_3)=0.2632$ .
}
\end{center}
\end{table}

### 2015-10-31 tables/tabNormNull_.tex
terminada polida na parte final

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 3 & 3 & 9 \\\hline
5.0 & 0.050 & 1.36 & 1 & 2 & 3 \\\hline
2.5 & 0.025 & 1.48 & 0 & 0 & 2 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for significance levels $\alpha$.
The $c_1$ values were calculated using simulations of normal distributions with $\mu=0$ and $\sigma=1$.
The $c_2$ values were calculated using simulations of normal distributions with $\mu=3$ and $\sigma=2$.
The $c_3$ values were calculated using simulations of normal distributions with $\mu=6$ and $\sigma=3$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.6527$ and $\sigma(c_1)=0.2398$,
 $\mu(c_2)=0.6889$ and $\sigma(c_2)=0.2397$,
 $\mu(c_3)=0.7184$ and $\sigma(c_3)=0.2811$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline\hline
10.0 & 0.100 & 1.22 & 7 & 10 & 8 \\\hline
5.0 & 0.050 & 1.36 & 5 & 3 & 4 \\\hline
2.5 & 0.025 & 1.48 & 3 & 1 & 3 \\\hline
1.0 & 0.010 & 1.63 & 0 & 1 & 3 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 1 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for significance levels $\alpha$.
The $c_1$ values were calculated using simulations of normal distributions with $\mu=0$ and $\sigma=1$.
The $c_2$ values were calculated using simulations of normal distributions with $\mu=3$ and $\sigma=2$.
The $c_3$ values were calculated using simulations of normal distributions with $\mu=6$ and $\sigma=3$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.8218$ and $\sigma(c_1)=0.2515$,
 $\mu(c_2)=0.7811$ and $\sigma(c_2)=0.2748$,
 $\mu(c_3)=0.8365$ and $\sigma(c_3)=0.2523$ .
}
\end{center}
\end{table}

### 2015-10-31 tables/tabPowerNull.tex
terminada polida na parte final

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ & $|C_5(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 5 & 5 & 7 & 5 & 5 \\\hline
5.0 & 0.050 & 1.36 & 2 & 3 & 5 & 1 & 1 \\\hline
2.5 & 0.025 & 1.48 & 1 & 2 & 1 & 1 & 0 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 1 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The $c_1$ values were calculated using simulations of power functions distributions with $a=0.3$.
The $c_2$ values were calculated using simulations of power functions distributions with $a=1$.
The $c_3$ values were calculated using simulations of power functions distributions with $a=2$.
The $c_4$ values were calculated using simulations of power functions distributions with $a=3$.
The $c_5$ values were calculated using simulations of power functions distributions with $a=4$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.6883$ and $\sigma(c_1)=0.2617$,
 $\mu(c_2)=0.7701$ and $\sigma(c_2)=0.2432$,
 $\mu(c_3)=0.7871$ and $\sigma(c_3)=0.2592$ .
 $\mu(c_4)=0.7721$ and $\sigma(c_4)=0.2587$ .
 $\mu(c_5)=0.7008$ and $\sigma(c_5)=0.2463$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ & $|C_5(\alpha)|$ \\\hline
100.0 & 0.100 & 1.22 & 79 & 76 & 74 & 81 & 78 \\\hline
50.0 & 0.050 & 1.36 & 36 & 33 & 32 & 38 & 35 \\\hline
25.0 & 0.025 & 1.48 & 17 & 10 & 21 & 19 & 15 \\\hline
10.0 & 0.010 & 1.63 & 8 & 2 & 8 & 6 & 8 \\\hline
5.0 & 0.005 & 1.73 & 3 & 1 & 3 & 1 & 7 \\\hline
1.0 & 0.001 & 1.95 & 1 & 0 & 1 & 0 & 2 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The $c_1$ values were calculated using simulations of power functions distributions with $a=0.3$.
The $c_2$ values were calculated using simulations of power functions distributions with $a=1$.
The $c_3$ values were calculated using simulations of power functions distributions with $a=2$.
The $c_4$ values were calculated using simulations of power functions distributions with $a=3$.
The $c_5$ values were calculated using simulations of power functions distributions with $a=4$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.8202$ and $\sigma(c_1)=0.2610$,
 $\mu(c_2)=0.8279$ and $\sigma(c_2)=0.2492$,
 $\mu(c_3)=0.8226$ and $\sigma(c_3)=0.2620$ .
 $\mu(c_4)=0.8216$ and $\sigma(c_4)=0.2596$ .
 $\mu(c_5)=0.8202$ and $\sigma(c_5)=0.2602$ .
}
\end{center}
\end{table}

### 2015-10-31 tables/tabPowerNull_.tex
terminada polida na parte final

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ & $|C_5(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 5 & 5 & 7 & 5 & 5 \\\hline
5.0 & 0.050 & 1.36 & 2 & 3 & 5 & 1 & 1 \\\hline
2.5 & 0.025 & 1.48 & 1 & 2 & 1 & 1 & 0 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 1 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The $c_1$ values were calculated using simulations of power functions distributions with $a=0.3$.
The $c_2$ values were calculated using simulations of power functions distributions with $a=1$.
The $c_3$ values were calculated using simulations of power functions distributions with $a=2$.
The $c_4$ values were calculated using simulations of power functions distributions with $a=3$.
The $c_5$ values were calculated using simulations of power functions distributions with $a=4$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.6883$ and $\sigma(c_1)=0.2617$,
 $\mu(c_2)=0.7701$ and $\sigma(c_2)=0.2432$,
 $\mu(c_3)=0.7871$ and $\sigma(c_3)=0.2592$ .
 $\mu(c_4)=0.7721$ and $\sigma(c_4)=0.2587$ .
 $\mu(c_5)=0.7008$ and $\sigma(c_5)=0.2463$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ & $|C_5(\alpha)|$ \\\hline\hline
10.0 & 0.100 & 1.22 & 6 & 12 & 12 & 9 & 7 \\\hline
5.0 & 0.050 & 1.36 & 6 & 3 & 5 & 4 & 2 \\\hline
2.5 & 0.025 & 1.48 & 2 & 0 & 1 & 2 & 1 \\\hline
1.0 & 0.010 & 1.63 & 1 & 0 & 1 & 1 & 0 \\\hline
0.5 & 0.005 & 1.73 & 1 & 0 & 1 & 1 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The $c_1$ values were calculated using simulations of power functions distributions with $a=0.3$.
The $c_2$ values were calculated using simulations of power functions distributions with $a=1$.
The $c_3$ values were calculated using simulations of power functions distributions with $a=2$.
The $c_4$ values were calculated using simulations of power functions distributions with $a=3$.
The $c_5$ values were calculated using simulations of power functions distributions with $a=4$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.8253$ and $\sigma(c_1)=0.2697$,
 $\mu(c_2)=0.8470$ and $\sigma(c_2)=0.2557$,
 $\mu(c_3)=0.8799$ and $\sigma(c_3)=0.2588$ .
 $\mu(c_4)=0.8278$ and $\sigma(c_4)=0.2637$ .
 $\mu(c_5)=0.7795$ and $\sigma(c_5)=0.2364$ .
}
\end{center}
\end{table}

### 2015-10-31 tables/tabUniformNull.tex
terminada polida na parte final

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 5 & 3 & 3 \\\hline
5.0 & 0.050 & 1.36 & 4 & 1 & 2 \\\hline
2.5 & 0.025 & 1.48 & 2 & 1 & 1 \\\hline
1.0 & 0.010 & 1.63 & 1 & 1 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The $c_1$ values were calculated using simulations of uniform distributions within $[0,1)$.
The $c_2$ values were calculated using simulations of uniform distributions within $[2,6)$.
The $c_3$ values were calculated using simulations of uniform distributions with $\mu=4$ and $\sigma=10$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.7656$ and $\sigma(c_1)=0.2552$,
 $\mu(c_2)=0.7520$ and $\sigma(c_2)=0.2421$,
 $\mu(c_3)=0.7077$ and $\sigma(c_3)=0.2250$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
100.0 & 0.100 & 1.22 & 93 & 88 & 95 \\\hline
50.0 & 0.050 & 1.36 & 43 & 42 & 39 \\\hline
25.0 & 0.025 & 1.48 & 19 & 28 & 17 \\\hline
10.0 & 0.010 & 1.63 & 7 & 10 & 12 \\\hline
5.0 & 0.005 & 1.73 & 4 & 4 & 8 \\\hline
1.0 & 0.001 & 1.95 & 1 & 0 & 1 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The $c_1$ values were calculated using simulations of uniform distributions within $[0,1)$.
The $c_2$ values were calculated using simulations of uniform distributions within $[2,6)$.
The $c_3$ values were calculated using simulations of uniform distributions with $\mu=4$ and $\sigma=10$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.8374$ and $\sigma(c_1)=0.2642$,
 $\mu(c_2)=0.8377$ and $\sigma(c_2)=0.2623$,
 $\mu(c_3)=0.8406$ and $\sigma(c_3)=0.2696$ .
}
\end{center}
\end{table}

### 2015-10-31 tables/tabUniformNull_.tex
terminada polida na parte final

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 5 & 3 & 3 \\\hline
5.0 & 0.050 & 1.36 & 4 & 1 & 2 \\\hline
2.5 & 0.025 & 1.48 & 2 & 1 & 1 \\\hline
1.0 & 0.010 & 1.63 & 1 & 1 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The $c_1$ values were calculated using simulations of uniform distributions within $[0,1)$.
The $c_2$ values were calculated using simulations of uniform distributions within $[2,6)$.
The $c_3$ values were calculated using simulations of uniform distributions with $\mu=4$ and $\sigma=10$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.7656$ and $\sigma(c_1)=0.2552$,
 $\mu(c_2)=0.7520$ and $\sigma(c_2)=0.2421$,
 $\mu(c_3)=0.7077$ and $\sigma(c_3)=0.2250$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline\hline
10.0 & 0.100 & 1.22 & 9 & 8 & 8 \\\hline
5.0 & 0.050 & 1.36 & 4 & 3 & 3 \\\hline
2.5 & 0.025 & 1.48 & 1 & 2 & 2 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 2 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 1 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The $c_1$ values were calculated using simulations of uniform distributions within $[0,1)$.
The $c_2$ values were calculated using simulations of uniform distributions within $[2,6)$.
The $c_3$ values were calculated using simulations of uniform distributions with $\mu=4$ and $\sigma=10$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.8616$ and $\sigma(c_1)=0.2291$,
 $\mu(c_2)=0.8345$ and $\sigma(c_2)=0.2492$,
 $\mu(c_3)=0.8086$ and $\sigma(c_3)=0.2740$ .
}
\end{center}
\end{table}

### 2015-10-31 tables/tabWeibullNull.tex
terminada polida na parte final

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 0 & 2 & 0 & 4 \\\hline
5.0 & 0.050 & 1.36 & 0 & 1 & 0 & 1 \\\hline
2.5 & 0.025 & 1.48 & 0 & 0 & 0 & 0 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The $c_1$ values were calculated using simulations of 1-parameter Weibull distributions with $a=0.1$.
The $c_2$ values were calculated using simulations of 1-parameter Weibull distributions with $a=2$.
The $c_3$ values were calculated using simulations of 1-parameter Weibull distributions with $a=4$.
Over all $N_c$ comparisons,
The $N_o$ values of $c_4$ were calculated using simulations of
 1-parameter Weibull distributions with $a=6$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.0548$ and $\sigma(c_1)=0.0314$,
 $\mu(c_2)=0.6878$ and $\sigma(c_2)=0.2352$,
 $\mu(c_3)=0.7030$ and $\sigma(c_3)=0.2037$ .
 $\mu(c_4)=0.7350$ and $\sigma(c_4)=0.2510$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ \\\hline
100.0 & 0.100 & 1.22 & 0 & 87 & 69 & 73 \\\hline
50.0 & 0.050 & 1.36 & 0 & 47 & 31 & 25 \\\hline
25.0 & 0.025 & 1.48 & 0 & 19 & 17 & 13 \\\hline
10.0 & 0.010 & 1.63 & 0 & 7 & 6 & 4 \\\hline
5.0 & 0.005 & 1.73 & 0 & 3 & 4 & 1 \\\hline
1.0 & 0.001 & 1.95 & 0 & 1 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The $c_1$ values were calculated using simulations of 1-parameter Weibull distributions with $a=0.1$.
The $c_2$ values were calculated using simulations of 1-parameter Weibull distributions with $a=2$.
The $c_3$ values were calculated using simulations of 1-parameter Weibull distributions with $a=4$.
Over all $N_c$ comparisons,
The $N_o$ values of $c_4$ were calculated using simulations of
 1-parameter Weibull distributions with $a=6$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.0289$ and $\sigma(c_1)=0.0179$,
 $\mu(c_2)=0.8306$ and $\sigma(c_2)=0.2660$,
 $\mu(c_3)=0.8001$ and $\sigma(c_3)=0.2520$ .
 $\mu(c_4)=0.8043$ and $\sigma(c_4)=0.2530$ .
}
\end{center}
\end{table}

### 2015-10-31 tables/tabWeibullNull_.tex
terminada polida na parte final

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 0 & 2 & 0 & 4 \\\hline
5.0 & 0.050 & 1.36 & 0 & 1 & 0 & 1 \\\hline
2.5 & 0.025 & 1.48 & 0 & 0 & 0 & 0 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The $c_1$ values were calculated using simulations of 1-parameter Weibull distributions with $a=0.1$.
The $c_2$ values were calculated using simulations of 1-parameter Weibull distributions with $a=2$.
The $c_3$ values were calculated using simulations of 1-parameter Weibull distributions with $a=4$.
Over all $N_c$ comparisons,
The $N_o$ values of $c_4$ were calculated using simulations of
 1-parameter Weibull distributions with $a=6$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.0548$ and $\sigma(c_1)=0.0314$,
 $\mu(c_2)=0.6878$ and $\sigma(c_2)=0.2352$,
 $\mu(c_3)=0.7030$ and $\sigma(c_3)=0.2037$ .
 $\mu(c_4)=0.7350$ and $\sigma(c_4)=0.2510$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ \\\hline\hline
10.0 & 0.100 & 1.22 & 0 & 10 & 6 & 6 \\\hline
5.0 & 0.050 & 1.36 & 0 & 4 & 2 & 4 \\\hline
2.5 & 0.025 & 1.48 & 0 & 0 & 1 & 2 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 1 & 2 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 2 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 1 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The $c_1$ values were calculated using simulations of 1-parameter Weibull distributions with $a=0.1$.
The $c_2$ values were calculated using simulations of 1-parameter Weibull distributions with $a=2$.
The $c_3$ values were calculated using simulations of 1-parameter Weibull distributions with $a=4$.
Over all $N_c$ comparisons,
The $N_o$ values of $c_4$ were calculated using simulations of
 1-parameter Weibull distributions with $a=6$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.1073$ and $\sigma(c_1)=0.0686$,
 $\mu(c_2)=0.8285$ and $\sigma(c_2)=0.2486$,
 $\mu(c_3)=0.7891$ and $\sigma(c_3)=0.2334$ .
 $\mu(c_4)=0.8063$ and $\sigma(c_4)=0.2845$ .
}
\end{center}
\end{table}
